This page and the next page should be removed

### 2021-01-07 analysis/master_thesis.tex
proofread + apa7 figure captions

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{}
\usepackage{csquotes}
\setcounter{tocdepth}{2}
\raggedbottom
\linespread{1.5}
\geometry{a4paper,margin=25mm}
\fancyhead{}
\fancyheadoffset[RO,LE]{0pt}
\fancyhead[RO,LE]{\thepage}
\fancyhead[LO,RE]{Semantic Knowledge and Unfamiliar Objects}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\doublespacing}
\captionsetup[figure]{font={stretch=1,scriptsize}}
\usepackage[all]{nowidow}
\usepackage[bottom]{footmisc}
\interfootnotelinepenalty=10000
\usepackage[export]{adjustbox}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\thispagestyle{empty}
\begin{center}
\vspace*{10mm}
\textbf{Event-Related Potentials of the Semantically Informed}\\
\textbf{Perception of Unfamiliar Objects}\\
\vspace*{5mm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
\end{center}
\end{figure}
{\setstretch{1.5}
Masterarbeit\\
an der\\
Humboldt-Universität zu Berlin\\
zur Erlangung des akademischen Grades \\
Master of Science (M.Sc.)\\
im Fach Psychologie\\
\vspace*{25mm}
}
\end{center}
\begin{flushleft}
{\setstretch{1.5}
\begin{tabular}{ll}
Vorgelegt von:&\textbf{Alexander Enge}\\
&geb. am 09.11.1996 in Räckelwitz\\
&Matrikelnummer 581331\\
Unter Betreuung von:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
&\\
Berlin, den 21.01.2021&\\
\end{tabular}
}
\end{flushleft}

@@

Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet. Lorem ipsum dolor sit amet, consetetur sadipscing elitr, sed diam nonumy eirmod tempor danke frederik invidunt ut labore et dolore magna aliquyam erat, sed diam voluptua. At vero eos et accusam et justo duo dolores et ea rebum. Stet clita kasd gubergren, no sea takimata sanctus est Lorem ipsum dolor sit amet.

@@

@@

\caption{Procedure and results of Experiment 1. \emph{(A)} In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing. In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception. In the post-insight part, the same objects were presented again without the keywords. \emph{(B)} ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts. Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part. Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}\label{fig:exp1-plot}
\end{figure}

@@

First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all furthere analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented). This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption. This was the case for an average of 27.0 objects per participant (= 44.9\% of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords \emph{and} if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of 48.8 objects per participant (= 81.2\% of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occurr---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).

The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018). For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages. First, they can account not only for the non-independence of data points coming from the same participant but also simultaneously for the non-independence of data points coming from the same item. In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012). Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions. Such a situation is inevitable in designs where the assignment of trials to conditions is (co-)determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).

Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively. All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.,~subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.,~subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition. For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to (Schad et al., 2020). To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013). We then performed a model selection algorithm as proposed by (Matuschek et al., 2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test. Only if the parsimonious model explained the data equally well as the complex model {[}determined by \emph{p} \textgreater{} .20; Matuschek et al. (2017){]} did we leave the random effect out, otherwise it was kept in the final model. All models were computed in R {[}Version 4.0.2; R Core Team (2020){]} using the lme4 package {[}Version 1.1.23; Bates et al. (2015){]}. The optimizer function \emph{bobyqa} with 20,000 iterations was used for maximum likelihood estimation. The model selection algorithm via likelihood ratio tests was performed using the buildmer package {[}Version 1.7.1; Voeten (2020){]}. Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts. All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package {[}Version 3.1.2; Kuznetsova et al. (2017){]}.

The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}). Unfortuntaly, lack of informed consent prevents us from sharing the raw EEG data.

@@

Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function. Only in the insight part, half of the objects were preceded by a matching description, fostering semantically informed perception to occur, whereas the other half were preceded by a non-matching description, leading to naive perception of the object. The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur. The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, in the N170 component (150--200 ms) as index of higher-level visual perception, and in the N400 component (400--700 ms) as an index of semantic processing.

@@

\caption{\label{tab:exp1-table}Results of linear mixed-effects regression models for Experiment 1}

@@

In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-inisight part) they were able to understand what kind of object they saw. To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.

In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms). When the same objects were presented once more in the post-insigt part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for whic semantically informed perception had taken place.

@@

All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1. An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses. Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with a non-matching description). Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).

@@

\caption{\label{tab:exp2-table}Results of linear mixed-effects regression models for Experiment 2}

@@

@@

\caption{Results of Experiment 2. ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment. In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-inisght part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064). Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}\label{fig:exp2-plot}
\end{figure}

@@

In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2. This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2. Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast {[}i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al. (2020){]}. This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes. They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2. Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).

@@

\caption{\label{tab:joint-table}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}

@@

Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Figure \ref{fig:joint-plot}). This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.

@@

@@

\caption{Measured and modelled ERP amplitudes for Experiments 1 and 2 combined. The violins and boxplots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred). The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval. Ampl. = amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.}\label{fig:joint-plot}
\end{figure}

@@

One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition. Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration. Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages. To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted. Instead of the naive condition (where objects were presented with non-matching descriptions), we now used those objects which were preceded by matching descriptions (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing. Across both experiments, this was the case for 49.6\% of objects presented with matching descriptions as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001. Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize. Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.

@@

Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400). Objects for which participants experienced semantically informed perception via matcing keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes. When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}
\caption{\label{tab:appendix}Unfamiliar Object Stimuli}\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/1.png} & 1 & elektrische Spannung prüfen & Makkaroni formen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/2.png} & 2 & Makkaroni formen & Kuh vom Zaun abhalten\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/3.png} & 3 & Knochen sägen & Streckenmaß Sonnenlicht nutzen\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/4.png} & 4 & Unkraut jäten & Uhr mit Wärme betreiben\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/5.png} & 5 & Mausefalle zuschnappen & Brillenglas zuschneiden\\
\includegraphics[valign=c, scale=0.2]{../materials/unfamiliar/6.png} & 6 & Goldmünzen wiegen & Farbe vom Fenster abschleifen\\

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{}
\usepackage{csquotes}
\geometry{a4paper,margin=25mm}
\setcounter{tocdepth}{2}
\raggedbottom
\usepackage{ragged2e}
\linespread{1.5}
\fancyhead{}
\fancyheadoffset[RO,LE]{0pt}
\fancyhead[RO,LE]{\thepage}
\fancyhead[RE,LO]{Semantic Knowledge and Unfamiliar Objects}
\usepackage{setspace}
\AtBeginEnvironment{tabular}{\doublespacing}
\captionsetup[table]{font={stretch=1.5}}
\captionsetup[figure]{font={stretch=1.5}}
\usepackage[all]{nowidow}
\usepackage[bottom]{footmisc}
\interfootnotelinepenalty=10000
\usepackage[export]{adjustbox}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\thispagestyle{empty}
\begin{center}
\vspace*{10mm}
\textbf{Event-Related Potentials of the Semantically Informed}\\
\textbf{Perception of Unfamiliar Objects}\\
\vspace*{5mm}
\begin{figure}[h]
\begin{center}
\includegraphics[width=!,totalheight=!,scale=0.25]{master_thesis_files/hu_logo}
\end{center}
\end{figure}
{\setstretch{1.5}
Masterarbeit\\
an der\\
Humboldt-Universität zu Berlin\\
zur Erlangung des akademischen Grades \\
Master of Science (M.Sc.)\\
im Fach Psychologie\\
\vspace*{25mm}
}
\end{center}
\begin{flushleft}
{\setstretch{1.5}
\begin{tabular}{ll}
Vorgelegt von:&\textbf{Alexander Enge}\\
&geb. am 09.11.1996 in Räckelwitz\\
&Matrikelnummer 581331\\
Fachliche Betreuung:&Prof. Dr. Rasha Abdel Rahman (Humboldt-Universität zu Berlin)\\
&Prof. Dr. Franziska Süß (Fachhochschule des Mittelstands)\\
&\\
Berlin, den 29.01.2021&\\
\end{tabular}
}
\end{flushleft}

@@

I would like to thank \ldots{} (tbc)

@@

\caption{Procedure and Results of Experiment 1\smallskip}\label{fig:exp1-plot}

@@

\bigskip\small\emph{Note.} 
(A) In the pre-insight part, participants were presented with 120 unfamiliar objects and indicated whether they knew what kind of object they were viewing. In the insight part, half of these objects were presented with matching keywords (in purple color for illustration), leading to semantically informed perception, and the other half with non-matching keywords (in petrol color for illustration), leading to naive perception. In the post-insight part, the same objects were presented again without the keywords. (B) ERP waveforms and scalp topographies are shown for objects with semantically informed versus naive perception within the three different parts. Semantically informed perception was associated with significantly more negative amplitudes in the N170 component in in the insight part, significantly less negative amplitudes in the N400 component in the insight and post-insight parts, and significantly more positive amplitudes in the P1 component in the post-insight part. Ampl. = amplitude.\newline
*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.

\end{figure}

@@

First, because we were interested in the effects of knowledge on perceiving \emph{unfamiliar} objects only, we excluded from all further analyses those objects which participants classified as being known to them in the pre-insight part (i.e.,~before any keywords were presented). This led to the exclusion of an average of 7.5 objects per participant (= 6.3\% of all unfamiliar objects). Next, to clearly delineate semantically informed and naive perception, the assignment of all other objects to one of these two conditions for statistical analyses was co-determined by our experimental manipulation (matching versus non-matching keywords in the insight part) and the behavioral responses of the participants themselves (see Figure \ref{fig:exp1-plot}A). Objects were assigned to the semantically informed condition only if they were presented with matching keywords \emph{and} if participants indicated knowing what the object was or having an assumption. This was the case for an average of 27.0 objects per participant (= 44.9\% of objects presented with matching keywords). Complementarily, objects were assigned to the naive condition only if they were presented with non-matching keywords \emph{and} if participants indicated not knowing what the object was or having rather no assumption. This was the case for an average of 48.8 objects per participant (= 81.2\% of objects presented with non-matching keywords). Although this assignment was based on the manipulation and responses in the second part---when insight was thought to occur---the same assignment was used to analyze the data from the other two parts. This allowed us to test, on the one hand, if the objects from both conditions differed in important aspects even before any keywords were presented (pre-insight part) and, on the other hand, if the semantic understanding acquired in the insight part had any lasting effects on a subsequent, third presentation of the objects (post-insight part).

The event-related potentials in response to objects from both conditions and all three parts were analyzed on the single trial level using linear mixed-effects regression models (Baayen et al., 2008; Frömer et al., 2018). For the purpose of the present study, these models have at least two desirable properties compared to traditional approaches such as analyses of variance (ANOVAs) performed on by-participant grand averages. First, they can account not only for the non-independence of data points coming from the same participant, but also simultaneously for the non-independence of data points coming from the same item. In contrast, the neglect of the item as a random variable in ANOVAs leads to anti-conservative test statistics and strictly does not allow for inferences beyond the stimulus set under study (Bürki et al., 2018; Judd et al., 2012). Second, mixed-effects models can flexibly deal with unbalanced designs in which the number of trials differs across (combinations of) conditions. Such a situation is inevitable in designs where the assignment of trials to conditions is co-determined by the experimental manipulation and the responses of the participants rather than by the experimental manipulation alone (e.g., Fröber et al., 2017).

Three separate models were computed predicting P1, N170, and N400 mean amplitudes, respectively. All models included three fixed effects: (a) the part of the experiment, coded as a repeated contrast (i.e.,~subtracting the first from the second part and the second from the third part, the intercept being the grand mean across all three parts), (b) the condition of the object, coded as a scaled sum contrast (i.e.,~subtracting the naive condition from the semantically informed condition, the intercept being the grand mean across both conditions), and (c) the two-way interaction of part and condition. For details on these and other contrast coding schemes in linear (mixed-effects) models, please refer to Schad et al. (2020). To determine the random effects structure, we always started with a maximal model containing by-participant and by-item random intercepts and random slopes for all fixed effects (Barr et al., 2013). We then performed a model selection algorithm as proposed by Matuschek et al. (2017) in order to increase statistical power and avoid overparameterization: Iteratively, each random effect was removed and the resulting, more parsimonious model was compared to the previous, more complex model by means of a likelihood ratio test. Only if the parsimonious model explained the data equally well as the complex model (determined by \emph{p} \textgreater{} .20; Matuschek et al., 2017) did we leave the random effect out, otherwise it was kept in the final model. All models were computed in R (Version 4.0.2; R Core Team, 2020) using the lme4 package (Version 1.1.23; Bates et al., 2015). The optimizer function \emph{bobyqa} with 20,000 iterations was used for maximum likelihood estimation. The model selection algorithm via likelihood ratio tests was performed using the buildmer package (Version 1.7.1; Voeten, 2020). Finally, to answer our research question of whether or not semantically informed perception had an influence on the ERP components within each part, planned follow-up comparisons were calculated, contrasting the informed against the naive condition within the pre-insight, insight, and post-insight parts. This was achieved using the emmeans package (Version 1.5.0; Lenth, 2020). All \emph{p}-values were computed by approximating the relevant denominator degrees of freedom using Satterthwaite's method as implemented in the lmerTest package (Version 3.1.2; Kuznetsova et al., 2017).

The materials, single trial behavioral and ERP data, and all code for data analysis can be accessed via the Open Science Framework (\url{https://osf.io/uksbc/}). Unfortunately, lack of informed consent prevents us from sharing the raw EEG data.

@@

Single-trial ERPs were analyzed in response to unfamiliar objects before (pre-insight part), while (insight part), and after (post-insight part) participants obtained relevant semantic information about their function. Only in the insight part, half of the objects were preceded by matching keywords, fostering semantically informed perception to occur, whereas the other half were preceded by non-matching keywords, keeping the perception of the object semantically naive. The objects were analyzed according to this manipulation in combination with participants' self-report in the insight part (see Figure \ref{fig:exp1-plot}A), thereby making sure that semantically informed and naive perception did indeed occur. The analysis focused on differences between these two conditions in the P1 component (100--150 ms) as an index of lower-level visual perception, the N170 component (150--200 ms) as index of higher-level visual perception, and the N400 component (400--700 ms) as an index of semantic processing.

@@

\caption{\label{tab:exp1-table}Results of Linear Mixed-Effects Regression Models for Experiment 1\smallskip}

@@

In Experiment 1, we measured event-related brain potentials from participants viewing unfamiliar objects before (pre-insight part), while (insight part) and after (post-insight part) they were able to understand what kind of object they saw. To induce this semantically informed perception, half of the objects in the insight part were preceded by matching verbal keywords about the object's typical function or use, whereas the other half were preceded by non-matching keywords, serving as a naive baseline condition.

In the insight part, we found that semantically informed perception was associated with enlarged amplitudes in the N170 component (150--200 ms after object onset) and reduced amplitudes in the N400 component (400--700 ms). When the same objects were presented once more in the post-insight part, the reduction of the N400 component reoccurred and we also observed a modulation of the P1 component (100--150 ms), which was significantly larger for objects for which semantically informed perception had taken place.

@@

All materials, procedures, EEG-related methods, and statistical analyses were identical to Experiment 1. An average of 7.0 objects per participant (= 5.8\% of all unfamiliar objects) was classified as being known in the pre-insight part and excluded from all further analyses. Based on participants' responses in the insight part, an average of 26.4 objects were assigned to the semantically informed condition (= 44.0\% of objects presented with matching keywords) and an average of 49.2 objects were assigned to the naive condition (= 82.0\% of objects presented with non-matching keywords). Automatic rejection of EEG epochs containing artifacts led to the exclusion of 11.0 trials per participant (= 3.0\%; range 0 to 85 trials).

@@

\caption{\label{tab:exp2-table}Results of Linear Mixed-Effects Regression Models for Experiment 2\smallskip}

@@

\caption{Results of Experiment 2\smallskip}\label{fig:exp2-plot}

@@

\bigskip\small\emph{Note.} 
ERP waveforms and scalp topographies are shown for objects for which participants experienced semantically informed versus naive perception within the pre-insight, insight, and post-insight parts of the experiment. In a direct replication of Experiment 1, the effect of semantic information on the N400 component in the insight and post-insight part and on the P1 component in post-insight part remained statistically significant, while the effect on the N170 component in the insight part remained only marginally significant (\emph{p} = .064). Ampl. = amplitude.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.

\end{figure}

@@

In an attempt to maximize statistical power, we combined the ERP data sets from Experiments 1 and 2. This allowed us to determine (a) if the above effects---including the marginally significant ones---were reliable when tested in a larger sample, and (b) if there were significant differences in the ERP amplitudes between Experiments 1 and 2. Methods for statistical analysis were kept unchanged apart from the addition of a new factor denoting the experiment, coded as a scaled sum contrast (i.e.,~subtracting Experiment 1 from Experiment 2, the intercept being the grand mean across both experiments; Schad et al., 2020). This factor and its possible interactions with part, condition, and part × condition were included in the linear mixed-effects regression models as fixed effects and as potential by-item random slopes. They were not included as by-participant random slopes since different participants took part in Experiments 1 and 2. Note that, as above, random effects were eventually included only if their omission led to a significant decline in model fit (Matuschek et al., 2017; Voeten, 2020).

@@

\caption{\label{tab:joint-table}Results of Linear Mixed-Effects Regression Models for Experiments 1 and 2 Combined\smallskip}

@@

Based on the part × condition interaction, we again computed follow-up comparisons between the semantically informed and the naive condition within each part, now collapsed across the data from both experiments (see Table \ref{tab:joint-table} and Figure \ref{fig:joint-plot}). This confirmed the absence of any reliable differences between the two conditions in the pre-insight part, all \emph{p}s \textgreater{} .577, the significant enhancement of the N170 component in the insight part, while the semantic information was obtained, \emph{b} = -0.57 µV, \emph{p} = .004, the significant reduction of the N400 component in the insight part, while the semantic information was obtained, \emph{b} = 1.10 µV, \emph{p} \textless{} .001, and in the post-insight part, after the information had been obtained, \emph{b} = 0.73 µV, \emph{p} \textless{} .001, as well as the significant enhancement of the P1 component in the post-insight part, after the information had been obtained, \emph{b} = 0.47 µV, \emph{p} = .014.

@@

\caption{Measured and Modeled ERP Amplitudes for Experiments 1 and 2 Combined\smallskip}\label{fig:joint-plot}

@@

\bigskip\small\emph{Note.} 
The violins and box plots show the distributions of the by-participant grand averaged ERPs during semantically informed perception (in purple color) and naive perception (in petrol color), separately for the pre-insight part (before insight was occurring), the insight part (while insight was occurring), and the post-insight (after insight had occurred). The yellow dots show the corresponding means of these conditions as predicted by linear mixed-effects modelling (see main text and Table \ref{tab:joint-table}), together with their respective 95\% confidence interval. Ampl. = amplitude, CI = confidence interval, LMM = linear mixed-effects model.\newline*\emph{p} \textless{} .05. **\emph{p} \textless{} .01. ***\emph{p} \textless{} .001.

\end{figure}

@@

One may raise concerns whether the modulation of the N170 component in the insight part genuinely reflects the semantically informed perception of the objects in the respective condition, or---as an alternative explanation---whether it may be driven by the objects in the other, semantically naive condition. Remember that these objects were preceded by non-matching keywords which were picked so that they could not be related to the visual features of the object and their configuration. Thus, the modulation of the ERP components in the insight part could be a mismatch response to those objects---reflecting, for example, the fact that the visual features of the object shown in Figure \ref{fig:exp1-plot}A cannot be reconciled with the function of morsing messages. To preclude this alternative explanation, we repeated our analysis using a different baseline against which the objects in the semantically informed condition were contrasted. Instead of the naive condition (where objects were presented with non-matching keywords), we now used those objects which were preceded by matching keywords (as in the informed condition), but which were excluded from the main analysis because participants indicated behaviorally that they did not understand the object they were seeing. Across both experiments, this was the case for 49.6\% of objects presented with matching keywords as compared to 44.4\% of objects which did indeed lead to semantically informed perception.\footnote{Note that these percentages do not add up to 100\% because some objects were excluded from all analyses because participants indicated knowing these objects in the pre-insight part, before any keywords had been presented (see Method).} Just as above, this control analysis revealed a robust N170 effect in the insight part, \emph{b} = -1.00 µV, \emph{p} \textless{} .001. Thus, this enhanced negativity seems to be a genuine marker of semantically informed perception, no matter if compared to objects presented with misleading keywords or compared to objects presented with accurate keywords but on which participants failed to capitalize. Note that the reduction of the N400 component in the insight part also remained robust in this control analysis, \emph{b} = 1.25 µV, \emph{p} \textless{} .001.

@@

Experiment 2, which was a direct replication of Experiment 1, confirmed the effects of obtaining semantic information about previously unfamiliar objects on ERPs associated with lower-level visual perception (P1), higher-level visual perception (N170), and semantic processing (N400). Objects for which participants experienced semantically informed perception via matching keywords elicited enlarged N170 amplitudes and reduced N400 amplitudes. When these objects were presented once more, they again elicited reduced N400 amplitudes as well as enlarged P1 amplitudes.

@@

\hypertarget{references}{%
\section{References}\label{references}}

\setlength{\cslhangindent}{0.5in}

\raggedright
\setlength{\cslhangindent}{0.5in}
